Attributions for Poverty in Post-Socialist Countries

### 2014-06-03 article2013.Rmd
tutzing videoluento purkissa..

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
affiliation: Finland
date: April 1, 2014
header-includes:
    - \usepackage{fancyhdr}
    - \pagestyle{fancy}
    - \fancyhead[CO,CE]{}
    - \fancyfoot[CO,CE]{}
    - \fancyfoot[LE,RO]{\thepage}
abstract: |
  Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in post-socialist countries of Europe and of Central and Western Asia. Citizens' attitudes towards the poor can be seen as reflecting the dominant ideology of country as well as the moral economy of the welfare state. Prior research has also shown that attributions for poverty have implications for the legitimacy of welfare system and for the viability of and support for anti-poverty policies.

>>>>

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
affiliation: Finland
date: June 2, 2014
header-includes:
    - \usepackage{fancyhdr}
    - \pagestyle{fancy}
    - \fancyhead[CO,CE]{}
    - \fancyfoot[CO,CE]{}
    - \fancyfoot[LE,RO]{\thepage}
abstract: |
  Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in post-socialist countries of Europe and of Central and Western Asia. Citizens' attitudes towards the poor can be seen as reflecting the dominant ideology of country as well as the moral economy of the welfare state. Prior research has also shown that attributions for poverty have implications for the legitimacy of welfare system and for the viability of and support for anti-poverty policies.
